Data Preparation

### 2021-07-22 paper.Rmd
v0.01 ... had to move to word (old school) as rendering got a complete mess :(

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(stats)
library(zoo)
library(patchwork)

@@

However, an evident question arises from this approach: what is the proper threshold for the service to be considered disrupted? Certain that, for some indicators, this could be a fixed value, this paper proposes an alternative method. The disruption threshold can be viewed as an adptive function of the recent traffic levels. As a result, the disruption threshold level would not be a fixed value, but a variable one, taking into account the recent trends to define a normal band based on moving windows. The example below shows this potential approach.
```{r}
#-------Remember to load and run "x0_data_preparation.Rmd". The object below is produced there!--------#
ResilienceMovingBands +
  theme(legend.position = "right")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(stats)
library(zoo)
library(patchwork)
library(roll)
library(sf)
library(countrycode)
library(ggnewscale)

@@

However, an evident question arises from this approach: what is the proper threshold for the service to be considered disrupted? Certain that, for some indicators, this could be a fixed value, this paper proposes an alternative method. The disruption threshold can be viewed as an adptive function of the recent traffic levels. As a result, the disruption threshold level would not be a fixed value, but a variable one, taking into account the recent trends to define a normal band based on moving windows. The example below shows this potential approach.

<<put band graph here>>

```{r}
# comparator levels
uplim  <- .80
lowlim <- .20
slide  <-  60

tmp <- us %>% 
  mutate( N_sm    = roll_quantile(N, width = 7, p = .50)
         ,MED     = roll_quantile(N, width = 14, p = .50, min_obs = 7)
         ,UP_THR  = roll_quantile(N, width = slide, p = uplim,  min_obs = 7)
         ,LOW_THR = roll_quantile(N, width = slide, p = lowlim, min_obs = 7)
         ,LOW_CRIT= LOW_THR >= MED
         ,UP_CRIT = UP_THR  <= MED
         ,STATE   = case_when( !LOW_CRIT & !UP_CRIT ~ "LEVEL"
                              , LOW_CRIT & !UP_CRIT ~ "CRUNCH"
                              ,!LOW_CRIT &  UP_CRIT ~ "RECOV" 
                              ,TRUE ~ "UNKWN")
         ,BAND    = 4000
         ) %>%
  filter(DATE >= lubridate::ymd("2019-10-01"))

###---------Rainer, the "new_scale_colour()" kinda resets the scale, and you can use another one for the next geom_lines. In the example below, I left the legend.position = "bottom" (instead of "NULL"), just to see the colors------###
Glass <- rgb(0, 0, 0, max = 255, alpha = 0, names = "transparent")

ResilienceMovingBands <- tmp %>%
  ggplot() +
  geom_line(aes(x = DATE, y = N), colour = "grey80") +
  geom_line(aes(x = DATE, y = N_sm, colour = THRES2, group = "RQ"), size = 2) +
  geom_line(aes(x = DATE, y = UP_THR), color = "blue") +
  geom_line(aes(x = DATE, y = LOW_THR), color = "red") +
  #geom_line(aes(x = DATE, y = MED), color = "forestgreen", size = 2) +
  #scale_color_brewer(type = "qual") +
  new_scale_colour() +
  geom_line(aes(x = DATE, y = BAND-100, group= "1"), colour = if_else(tmp$LOW_CRIT, "red",Glass), size = 4) +
  geom_line(aes(x = DATE, y = BAND+16000, group= "1"), colour = if_else(tmp$UP_CRIT, "blue", Glass), size = 4) +
  geom_line(aes(x = DATE, y = BAND-4000, group= "1", colour = STATE), size = 10) +
  scale_colour_manual(values = c("darkred", Glass, "darkblue")) +
  theme_minimal() +
  theme(legend.position = "bottom")

ResilienceMovingBands +
  theme(legend.position = "right")
```

### 2021-07-22 x0_data-preparation.Rmd
v0.01 ... had to move to word (old school) as rendering got a complete mess :(

base_filenames <- list.files("./data/", pattern = "base_osn_*")
base_fullnames <- c(paste0("./data/", base_filenames))
full_dataset <- map_dfr(base_fullnames, read_csv)

>>>>

base_filenames <- list.files("./data/", pattern = "base_osn_2*")
base_fullnames <- c(paste0("./data/", base_filenames))
full_dataset <- map_dfr(base_fullnames, read_csv)
